\documentclass{article}
\usepackage{scimisc-cv}
\usepackage{url}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

\title{Fan Ni's resume for Job}
\author{Fan Ni}
\date{Sept. 2020}

%% These are custom commands defined in scimisc-cv.sty
\cvname{Fan Ni, PhD}
\cvpersonalinfo{
4728 Granado Ave, Fremont, CA 94536\cvinfosep 
313-925-5065 \cvinfosep
nifan.man@gmail.com \cvinfosep
\it{https://www.linkedin.com/in/fan-ni-4b591049/}
}

\begin{document}

% \maketitle %% This is LaTeX's default title constructed from \title,\author,\date

\makecvtitle %% This is a custom command constructing the CV title from \cvname, \cvpersonalinfo

\section{Job interests}
I am now a research software engineer of the ATG group of the CTO office at NetApp. I have backgrounds and industry experience in both computer systems (storage systems and file systems) and computer architecture. I am particularly interested in \textbf{storage systems}, \textbf{file systems}, \textbf{infrastructure software}, \textbf{cloud systems}, and \textbf{GPU/CPU architecture related software development}, and any software development or research position in the above area is my target.

Note: relocation is an option for me if the position fits me.

\section{About me}
\begin{itemize}
    \item Loving coding and debugging. Using code to solve real problems has always been my wish. 
    \item Self-motivated, problem-solving and collaborative team worker, and eager to learn.
    \item A big fan of soccer and my favorable team is Arsenal from Premier League; used to play soccer a lot in university. 
    \item Like road trip and spending my spare time with friends.
    \item Holding \textbf{H1B} since 10/2019
\end{itemize}

\section{Education}
\begin{itemize}
\item PhD, Computer engineering,  University of Texas at Arlington, 2019
\item PhD, Computer systems organization, Beihang University, China , 2014
\item B.S., Computer science and technology, Beihang University, China,  2006
 %   \item 2016.01-2019.5 \hspace{1.2cm}  Ph.D, University of Texas at Arlington  \hspace{2cm} Computer Engineering
%    \item 2006.09-2014.3 \hspace{1.05cm}  Ph.D,  Beihang University, China        \hspace{2.75cm} Computer systems organization
%    \item 2002.09-2016.07 \hspace{0.9cm} Bachelor, Beihang University, China       \hspace{2.2cm} Computer science and technology
\end{itemize}


 
\section{Work Experience}

 %   \item 
    \begin{tabular}{lp{15cm}}
         2019.06-Present & \bf{Research Software Engineer, Advanced Technology Group (ATG), CTO office, NetApp, Sunnyvale, CA} \\
         & \small{\it Duties: 1) Exploring technique trends in storage technique field and generating technique reports which are accessible to the whole company; 
         2) Building prototype to evaluate new features or ideas in storage systems, and collaborating with product teams to deploy in the products if the feature or idea is adopted;
         3) Building relationship with universities for cutting-edge research; 
         4) Serving as PC member of international conferences (HotEdge, APSys) and reviewer of SCI journals. }\\
         2018.06-2018.08 & \bf{Research intern, Advanced Technology Group (ATG), CTO office, NetApp, Sunnyvale, CA}\\
         & \small{\it Duties: Designing and Developing parallel algorithms to leverage Intel AVX instructions for better chunking speed and better deduplication ratio in CDC-based deduplication systems;}\\
         2014.04-2015.12 &\bf{Research Fellow,  Inspur (Beijing) Electronic Information Industry Co., Beijing}\\
         & \small{\it Duties: Leading the architecture research team, doing large-scale CC-NUMA system research, including cache coherence optimization, system modelling and virtualization technology investigation for cloud computing environment;}\\
         2013.05-2013.08 & \bf {Research intern, AMD research China (Beijing), Beijing}\\
         &\small{\it Duties: Accelerating numerical functions in Numpy (a package for scientific computation in Python) with APPML (or clMagma) to explore the potential of APU in scientific computation; working with a full-time employee on new memory architecture design in APU;}\\
         2010.11-2011.07 & \bf{Test intern, Oracle (Sun ERI), Beijing} \\
         &\small{\it Duties: Designing test cases with C and shell and carrying them out on new Solaris release and testing new WIFI features.}
    \end{tabular}

\section{Projects}
%\small
\begin{enumerate}
\item (\textbf{Computational storage, SmartNIC, NFS, Key-value Store}) Using computational devices to enhance storage systems' performance: Leveraging computational devices (like SmartSSD, SmartNIC) to extend storage systems to provide better performance or save cost. As an example, with very weak CPUs in SmartNIC, we transparently improve the Get performance of rocksDB by over 20\% for some workloads by enabling a lightweight cache on SmartNIC.
\item (\textbf{File systems, Deduplication, Kernel development}) WOJ (Write-once journaling): Data journaling mode in Journaling file systems (Ext3, Ext4, etc.) doubles the writes, which can significantly compromise performance and shorten SSD's lifetime. WOJ is a method to apply weak-hash based deduplication to avoid the redundant writes without compromising data correctness. The mechanism is implemented at the Linux kernel block layer as a device mapper target, and about 50\% of writes are reduced and the performance is about 2.7$\times$ higher than the approach with regular deduplication approaches. A paper is accepted by IFIP Performance. 
\item (\textbf{Deduplication}) RapidCDC:  In deduplication systems, to detect duplicates usually we need first cut the input files into smaller units (chunks), on which duplicates are detected. The process is time-consuming for variable-size chunking as we need to check the input files byte-by-byte to determine a chunk bounary. In the project, we disclosed the existence of duplicate locality and leveraged the chunking history to accelerate the chunking process. The evaluation shows the chunking time can be reduced by more than 95\% for many real-work workloads, and a paper was accepted by SoCC.
\item (\textbf{Data structures, software cache, CPU cache, Gem5}) Accelerating tree traversal with software and hardware cache: trees have been widely used in many systems as the key data structures to provide infrastructure support. However, the accesses to tree structures can be expensive as we need to traverse from the head to the leaf, which can be tens of memory accesses. In the project, we proposed both software and hardware cache solutions (SLB and SDC) to accelerate tree search by caching the search results directlly in a software cache or in CPU cache with key-value style interface. In both designs, we overcome many technique challenges, like how to process mapping collisions and data replacement.
\item (\textbf{SSD, Key-value Store, Deduplication, Kernel development}) Freewrite: In LSM-based key-value stores (like LevelDB), the SSTables in a level needs to be merged from time to time and pushed to the next level (called compaction). The process can introduce high write amplification, which will hurt both performance and data devices' lifetime if the devices are SSD. In the project, we re-designed the layout of SSTables, and allowed some space ("bubbles") in each page unfilled to avoid the data content shift across different pages during compaction. Also, at the block-layer we use block-level deduplication to detect duplicate page writes.
For the evaluation, we modified LevleDB and implemented a deduplication scheme at the block layer as a device mapper target, and the results showed the throughput can be improved by 26\%.
\item (\textbf{CPU cache, Architecture Simulation, Gem5}) Cache coherence protocol simulation for Large-scale CC-NUMA systems: Established a simulation system with Gem5 to simulate advanced cache coherence protocol used in complex large-scale CC-NUMA system and was award \textbf{platinum award} from Inspur, which was very rare for first year employee.
\item (\textbf{Architecture Simulation, OS, Embedded Systems, Parallel Programming})	PCSim: We (A student I mentored and I) designed a parallel simulator targeting Freescale MPC8641D platform. The simulator was able to boot tailored Linux OS and complete cross-ISA embedded software testing and debugging. In the project, we need to customize the boot loader (uboot) and the Linux OS to run on the simulator.
\item (\textbf{GPU, CUDA programming, Architecture simulation})	Built a parallel cache simulator on NVIDIA CUDA platform (2007, CUDA 1.0). 
Several design challenges are tackled, like the global synchronization among threads in multiple thread sets, and trade-off between parallelism and synchronization overhead.
\end{enumerate}

\section{Selected recent publications (since 2016), \href{https://scholar.google.com/citations?user=xMbxve0AAAAJ&hl=en}{full list}}
\begin{enumerate}
\small
\it
    \item \textbf{Fan Ni} and Song Jiang, "RapidCDC: Leveraging Duplicate Locality to Accelerate Chunking in CDC-based Deduplication Systems", in Proceedings of 2019 ACM Symposium on Cloud Computing (ACM SoCC'19), Santa Cruz, CA, November, 2019.[\href{https://github.com/moking/RapidCDC}{code}]
    \item \textbf{Fan Ni}, Xingbo Wu, Weijun Li, Lei Wang, and Song Jiang, “Leveraging SSD's Flexible Address Mapping to Accelerate Data Copy Operations”, in Proceedings of the IEEE 21st International Conference on High Performance Computing and Communications; (HPCC-2019), Zhangjiajie, China, August, 2019.
    \item \textbf{Fan Ni}, Song Jiang, Hong Jiang, Xingbo Wu, and Jian Huang, “SDC: A Software Defined Cache Supporting Flexible Key-value-style Data Caching”, in Proceedings of the 33th ACM International Conference on Supercomputing (ICS'19), Phoenix, AZ, June, 2019.
\item \textbf{Fan Ni}, Xing Lin, and Song Jiang, “SS-CDC: A Two-stage Parallel Content-Defined Chunking for Deduplicating Backup Storage", in Proceedings of the 12th ACM International Systems and Storage Conference (SYSTOR'19), Haifa, Israel, June, 2019.[\href{https://github.com/NetApp/SS-CDC}{code}]
\item Xingbo Wu, \textbf{Fan Ni}, and Song Jiang, "Wormhole: A Fast Ordered Index for In-memory Data Management", in Proceedings of the European Conference on Computer Systems (EuroSys'19), Dresden, Germany, March, 2019. [\href{https://github.com/wuxb45/wormhole}{code}]
\item \textbf{Fan Ni}, Xingbo Wu, Weijun Li, Lei Wang, and Song Jiang. "WOJ: Enabling Write-Once Full-data Journaling in SSDs by using weak-hashing-based deduplication." Performance Evaluation (IFIP Performance 2018).
\item \textbf{Fan Ni}, Xingbo Wu, Weijun Li, and Song Jiang. “ThinDedup: An I/O Deduplication Scheme that Minimizes Efficiency Loss due to Metadata Writes”, in Proceedings of the 37th IEEE International Performance Computing and Communications Conference (IPCCC'18), Orlando, Florida, November 2018. (\textbf{\it \textbf{Best Paper Candidate}})
\item Xingbo Wu, \textbf{Fan Ni}, Song Jiang. Search Lookaside Buffer: Efficient Caching for Index Data Structures [SoCC'17] ACM Symposium on Cloud Computing 2017
\item Chunyi Liu, \textbf{Fan Ni}, Xingbo Wu, Xiao Zhang, Song Jiang. Freewrite: Creating (Almost) Zero-Cost Writes to SSD in Applications [SYSTOR'17] The 10th ACM International Systems and Storage Conference
\item \textbf{Fan Ni}, Chunyi Liu, Yang Wang, Chengzhong Xu, Xiao Zhang, Song Jiang. A Hash-based Space-efficient Page-level FTL for Large-capacity SSDs [NAS'17] 12th International Conference on Networking, Architecture, and Storage (NAS)
\item Xingbo Wu, \textbf{Fan Ni}, Li Zhang, Yandong Wang, Yufei Ren, Michel Hack, Zili Shao, Song Jiang. NVMcached: An NVM-based Key-Value Cache [APSys'16] 7th ACM SIGOPS Asia-Pacific Workshop on Systems.
\item \textbf{NOTE}: More publications on \textbf{computer architecture} before 2016 can be found \href{https://scholar.google.com/citations?user=xMbxve0AAAAJ&hl=en}{here}.
\end{enumerate}
    

\section{Patents}
\begin{itemize}
    \item “Methods for optimized variable-size deduplication using two stage content-defined
chunking and devices thereof”, US20200081868A1
    \item I have about 10 China patents filed or granted.
\end{itemize}



\section{Professional Skills}
\begin{enumerate}
\item	Very good C programming skill. C is my main working language during my research and my work. I am also familiar with C++.
\item	Familiar with Python and Shell programming.
\item	Familiar with Linux Kernel knowledge and have worked in the device mapper framework to develop some new I/O features.
\item	Experience with compiler-related developing. Worked in LLVM framework to enabling binary translation for an ARM simulator. 
\item	Experience of CUDA programming. Built a parallel cache simulator on CUDA platform.
\item	Familiar with data structures, including array, linked list, hash table, trees, heap, etc.
\item   Familiar with KV cache (MemCached) and KV store (LevelDB) design.
\item	Network programming experience (libuv).
\end{enumerate}

% \section{Other Skills}
% \begin{description}[widest=Langauges]
% %\item[Software]	GraphPad Prism, Microsoft Word, Excel, and PowerPoint, ImageJ
% \item[Languages]	English: professional proficiency.  Mandarin: native.  
% \end{description}



\end{document}
